%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Cover Letter
% XeLaTeX Template
% Version 1.1 (9/1/2016)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original authors:
% Claud D. Park (posquit0.bj@gmail.com)
% Lars Richter (mail@ayeks.de)
% With modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template must be compiled with XeLaTeX, the below lines will ensure this
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm} % Configure page margins with geometry

\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\colorlet{awesome}{awesome-red} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------


\name{Kristan}{Bullett}
\address{York, United Kingdom}
\mobile{(+44) 7899 795 937}

\email{kristan@bullett.org.uk}
%\homepage{www.posquit0.com}
%\github{posquit0}
\linkedin{kristanbullett}
\skype{kristan@bullett.org.uk}
%\skype{skypeid}
%\stackoverflow{SOid}{SOname}
%\twitter{@twit}
%\linkedin{linkedin name}
%\reddit{reddit account}
%\xing{xing name}
%\extrainfo{test} % Other text you want to include on this line

\position{Digital Innovation{\enskip\cdotp\enskip}Technology Evangelist} % Your expertise/fields
\quote{``Energetic \& confident executive with extensive experience in senior technical and strategic leadership positions. Concentrating heavily for nearly 20 years in the Media \& Entertainment space, specifically working with IP based VOD technologies delivering multi-million dollar projects across multiple countries. Broad understanding of metadata management \& optimisation with a proven track record of successfully leveraging and implementing transformative solutions. Excellent client manner bridging the gap between business and technical stakeholders. Focussed on creating an exceptional work ethic at all levels in teams, and identifying and exploiting individuals’ strengths.”} % A quote or statement

%----------------------------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------

\recipient{.}{.}
%\recipient{Company Recruitment Team}{Initech Inc.\\4120 Freidrich Ln.\\Austin, TX 78744} % The company being applied to

\letterdate{\today} % The date on the letter, default is the date of compilation

\lettertitle{Application for role of Head of Media Engineering} % The title of the letter

\letteropening{Dear Sir / Madam,} % How the letter is opened

\letterclosing{Sincerely,} % How the letter is closed

%\letterenclosure[Attached]{Curriculum Vitae} % Any enclosures with the letter

\makecvfooter{\today}{Kristan Bullett~~~·~~~Cover Letter}{} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed

%----------------------------------------------------------------------------------------

\begin{document}

\makecvheader % Print the header

\makelettertitle % Print the title

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\begin{cvletter}

%------------------------------------------------

\lettersection{About Me}

With nearly 20 years’ experience in building and leading technical teams, I am currently Managing Director of Piksel Ltd, a Product-led Services company specialising in providing a SaaS video platform focussed on metadata management, playout services and workflow orchestration tooling. Previously, within the same company, I held the positions of Head of Solutions and Head of Architecture. I continue to maintain a very technically focussed position, hold a passion for both digital and business transformation and have strong and broad industry knowledge.

%------------------------------------------------

\lettersection{Why Me?}

Strong, modern technical teams need to be built on core philosophical and technical foundations including considerations for,

\vspace{3.4mm}

\begin{cvitems}
\item {Continuous Delivery}
\item {DevOps}
\item {Business-capability centric teams}
\item {Data-driven analysis}
\item {Micro-service architectures}
\item {Management by exception, and}
\item {Continuous Improvement}
\end{cvitems}

\vspace{3.4mm}

I believe my strong technical background, in combination with my extensive experience working with executive leader- ship teams, puts me in a unique position to bridge the gap between building and leading technical teams and working with senior management, to articulate the need for and to attain the buy-in for significant technical change.
Through strong technical transformation, focus can be shifted from resolving technical barriers to delivering technical platforms that provide flexibility and agility and enable the business to focus on core growth objectives.
Based on my experience and passions I believe I am well placed to lead this kind of transformation for NBCU.

%------------------------------------------------

\end{cvletter}

%----------------------------------------------------------------------------------------

\makeletterclosing % Print the signature and enclosures

\end{document}
