%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cvexpentry
{Managing Director} % Job title
{Piksel} % Organization
{York \& London, UK and international} % Location
{Mar. 2018 - present} % Date(s)
{
\begin{cvitemstitle}
\item {As part of the Piksel executive team, and co-Managing Director, taking responsibility for the Media \& Entertainment vertical. Particular focus is placed on defining the commercial strategy and product market, managing partnerships, reducing operational costs, transforming team culture and driving growth with product revenue growing >400\% since 2017.}
\end{cvitemstitle}
}
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {P\&L responsibility with particular focus on taking a data driven approach to understanding Piksel as a business}
\item {Introduced and enforced Salesforce to enable clear understanding of Lead, Prospect and Opportunities and Pipeline}
\item {Established JIRA as a tool to manage improvement activities across sales and marketing and customer success}
\item {Restructured sales and marketing to half overall budget whilst ensuring the activity throughput becomes tracked, focussed and effective output is increased}
\item {Shifted event focus from low-engagement, high-cost sponsored marketing events to relevant event attendance with active contributions including panel talks, presentations and industry body contributions}
\item {Halved sales and marketing costs whilst increasing tracked sales pipeline by 100\% in a 12 month period}
\end{cvitems}
}

%------------------------------------------------

\cvexpentry
{Head of Solutions} % Job title
{Piksel} % Organization
{York \& London, UK} % Location
{Mar. 2017 - present} % Date(s)
{
\begin{cvitemstitle}
\item {As Head of Solutions, responsible for all pre-sales and post-sales engagements globally for Piksel SaaS Product(s), along with being part of the Piksel executive team. Hybrid role which provides thought leadership, evangelism, organisational change and continual improvement philosophies both internally and externally.}
\end{cvitemstitle}
}
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Leading commercial and technical pre-sales go to market strategies and service offerings for Piksel SaaS Product(s)}
\item {Owned the technical due diligence for key M\&A activities}
\item {Drove organisational and technical transformation by establishing companywide technical guilds, architectural forums, weekly lightning talks and regular lunch and learn activities}
\item {Continued and active responsibility for growing multi-\$mm customers including Liberty Global, Discovery Communications, Channel 4, AT\&T, A+E Networks, Sky, OSN and beIN Sports with demonstrable increase in average customer value and decrease in customer churn}
\item {Led operational restructure to merge disparate delivery functions into a single cohesive unit for customer success across technical, commercial, implementation and service delivery}
\end{cvitems}
}

%------------------------------------------------

\cvexpentry
{Head of Architecture} % Job title
{Piksel} % Organization
{York \& London, UK} % Location
{Aug. 2013 - Mar. 2017} % Date(s)
{
\begin{cvitemstitle}
\item {As Group Head of Architecture for Piksel, reporting directly to the CTO and COO (split) with responsibility for technical leadership across both professional services and the commercial organisation. Involves leading a team of 20+ Technical and Solution Architects globally.}
\end{cvitemstitle}
}
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Improved staff retention \& motivation through mix of activities including, re-writing job descriptions, clearly articulating career paths and enforcing regular employee one on ones}
\item {Led mentoring and career progression program}
\item {Improved customer satisfaction through establishing customer satisfaction surveys and subsequent improvement initiatives based on feedback}
\item {Creation of a unified and global Professional Service organisation}
\item {Established a culture of knowledge sharing and nurturing a culture of ideas \& innovation through execution of innovation workshops across all offices}
\item {Defined and set technical direction (tooling, languages, frameworks)}
\item {Ensuring a set of Agile processes are introduced across all projects}
\item {Representing Piksel at various industry events including IBC, CES, NAB and TV Connect}
\end{cvitems}
}

%------------------------------------------------

\cvexpentry
{VP Architecture, Senior Technical Architect} % Job title
{KIT Digital} % Organization
{London, UK; San Diego, US} % Location
{Apr. 2011 - Aug. 2013} % Date(s)
{
\begin{cvitemstitle}
\item {Extensive time spent taking technical responsibility for client deliveries for customers such as Liberty Global, UPC, The Discovery Channel, Telenet, UnityMedia, AT\&T, Sky, BBC, Channel 4, StarHUB, BAA Systems and IMS Healthcare.}
\end{cvitemstitle}
}
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\end{cvitems}
}

%------------------------------------------------

\cvexpentry
{Senior Technical Architect, Technical Architect, Technical Lead, Senior Developer} % Job title
{ioko} % Organization
{York \& London, UK; San Diego, US} % Location
{Aug. 2000 - Apr. 2011} % Date(s)
{
\begin{cvitemstitle}
\item {ioko are a start-up specialising in bespoke software development, managed services and system integrations.}
\end{cvitemstitle}
}
 %Top level description
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
