%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Projects}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{End to End Architect} % Role
{Horizon TV Online} % Project
{Amsterdam, Netherlands} % Location
{Oct. 2010 - Nov. 2013} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {Horizon TV is Liberty Global's global OTT platform. Kristan lead all technical aspects of this project as Lead End to End Architect. This was a complete green field engagement across a multi-phased delivery.}
\item {Responsibilities included Requirements Analysis, Domain Modelling, (extensive) System Integration, Fault Tolerance, Distributed Architecture, Software Automation, Vendor Management, Infrastructure Architecture, Agile Project Delivery, Technology selection and definition, management of 20+ delivery team, extensive pan-European travel.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Senior Architect} % Role
{AT\&T U-Verse Online} % Project
{San Antonio \& Dallas, US} % Location
{Jun. 2007 - Oct 2010} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {As a Senior Technical Architect, Kristan shared responsibility for the end to end delivery of the AT\&T U-Verse Online program. U-Verse Online is part of AT\&T’s strategy to make popular U-Verse content available to consumers across multiple screens, including the TV, PC and mobile devices. This project involved extensive system integration to customer platforms, databases, 3rd party payment servers, STB integration and integration with the likes of CBS, Hulu and MTV for content acquisition.}
\item {Key Skills included Java, Spring, Spring MVC, Hibernate, Sonar, Eclipse, Crucible, JIRA, Greenhopper, REST, SOAP, JavaScript, CSS, Freemarker, Interwoven TeamSite, Architecture, Technical Leadership, Requirements Capture, Technical Strategy, Extensive international client facing experience.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Technical Lead} % Role
{Sky by Broadband (now Sky Go / Now TV)} % Project
{London, UK} % Location
{Jun. 2007 - Oct 2010} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {Sky by Broadband (now Sky Go / Now TV) is BSkyB's flagship OTT platform, providing integrated OTT to BSkyB's 10 million customers. Kristan lead the delivery of all Client applciations and contributed heavily to the server aspects of the architecture.}
\item {Key Skills included Flash, C\#, Java, System Integration, Technology Selection, Requirements Analysis, Team Leadership, Extensive customer facing relationships.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
